Cheat Sheet for PFPL

### 2016-12-02 pfpl/draftcheatsheet.tex
Add application from chapter 18 reunumber Add Chapter 43

55& 157 & $::$ & Colon colon & Kind type constructor & Maps types to types \\
\end{tabular}
\subsection*{VIII. Partiality and Recursive Types}
\subsubsection*{19 System PCF of Recursive Functions}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

56& 166 & $\mapsto$ & Short bar arrow & Maps to & Function definition \\
57& 166 &$ \bot$ & Bottom & Bottom & Totally undefined partial function \\
58& 167 & $\tau_1 \rightharpoonup \tau_2$ & Harpoon & Partial function & Partial function \\
\end{tabular}

@@

59& 177 & $\_$ & Underscore & Underscore & Unfree variable \\
\end{tabular}
\subsection*{IX. Dynamic Types}
\subsubsection*{21 The Untyped $\lambda$-Calculus}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

60& 185 & $\Lambda$ & Lambda & Lambda calculus & The lambda calculus \\
61& 188 & Y & Y & Y Combinator & The Y combinator \\
62& 190 & $x^{\dagger}$ & Superscript cross & Superscript cross & Language isomorphism \\

@@

63& 213 & $\tau'<:\tau$ & Subtype & $\tau'$ is a subtype of $\tau$ & $\tau'$ is a subtype of $\tau$ \\

@@

64& 252 & $()^{\ddagger}$ & Isomorphism & Isomorphism & $()^{\ddagger}$ is a method isomorphism \\

@@

65& 257 & $k \vartriangleright e$ & Right triangle & Evaluation state & Evaluate $e$ on $k$ \\
66& 257 & $k \vartriangleleft e$ & Left triangle & Return state & Evaluate $k$ on $e$\\
67& 258 & $\epsilon$ & Epsilon & Empty frame & Empty frame\\
68& 258 & (\textemdash) & Frame hole & Frame hole & A place to put an evaluated expression into a frame\\
69& 258 & $k;f$ & Stack with frame & Stack $k$ with frame $f$  & Stack $k$ has frame $f$ at the bottom\\
70& 259 & $k \vartriangleleft:\tau$ & Triangle colon & Stack $k$ expects value of type $\tau$ & Stack $k$ expects value of type $\tau$\\
71& 259 & $f:\tau\rightsquigarrow\tau'$ & Squiggle arrow & Transform & Frame $f$ transforms expression of type $\tau$ into expression of type $\tau'$\\
72& 261 & $s \looparrowright e$ & Loop arrow & Unravel & State $s$ goes to expression $e$ \\
73& 261 & $k \bowtie e = e'$ & Bowtie & Goes to & Stack $k$ and expression $e$ goes to expression $e'$\\

@@

74& 266 & $k \blacklozenge$ & Dark left triangle & Failed & Stack $k$ is in a failed state \\

@@

75 & 282 & $a \sim \tau$ & Tilde & Define $a$ & Define symbol $a$ as type $\tau$ \\
76 & 282 & $\Sigma$ & Sigma & Symbol context & Set of symbol definitions \\
77 & 284 & $'a$ & Quote & Symbol reference & Symbol reference \\
\end{tabular}

\subsubsection*{32 Fluid Binding}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\
78 & 290 & $\mu ' \otimes a \hookrightarrow e$ & Tensor product & Extended by &  Map symbol $a$ to expression $e$\\
79 & 290 & $\mu ' \otimes a \hookrightarrow \bullet$ & Tensor product & Extended by &  Symbol $a$ is undefined\\
80 & 290 & $\mu ' \otimes a \hookrightarrow $ \underline{ } & Tensor product & Extended by &  Symbol $a$ is indeterminate\\

@@

81& 308 & $x \leftarrow e ; m$ & Left arrow & Sequence & Execute command $m$ with $e$ substituted for $x$ \\
82& 308 & $a := e$ & Colon equals & Assign & Assign $e$ to $a$\\
83 & 308 & $*a$ & Star & Contents & Get the value of $a$\\
84 & 309 & $ m \| \mu $& State & State & Command $m$ with memory map $\mu$\\
85 & 314 & $ m \thicksim \tau$ & Dotted tilde & Dotted tilde & Command $m$ returns a value of type $\tau$\\
\end{tabular}

@@

86 & 320 & $ \& a $ & Ampersand & Reference & Reference to assignable \\

@@

87 & 333 & $ \Longrightarrow $ & Long right arrow & Implies & Implication (low precedence) \\

>>>>

55& 157 & $::$ & Colon colon & Kind type constructor & Maps types to types \\
56 & 158 & $e_1[e_2] $ & Bracket & Application & Apply (call) function \\
\end{tabular}
\subsection*{VIII. Partiality and Recursive Types}
\subsubsection*{19 System PCF of Recursive Functions}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

57& 166 & $\mapsto$ & Short bar arrow & Maps to & Function definition \\
58& 166 &$ \bot$ & Bottom & Bottom & Totally undefined partial function \\
59& 167 & $\tau_1 \rightharpoonup \tau_2$ & Harpoon & Partial function & Partial function \\
\end{tabular}

@@

60& 177 & $\_$ & Underscore & Underscore & Unfree variable \\
\end{tabular}
\subsection*{IX. Dynamic Types}
\subsubsection*{21 The Untyped $\lambda$-Calculus}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

61& 185 & $\Lambda$ & Lambda & Lambda calculus & The lambda calculus \\
62& 188 & Y & Y & Y Combinator & The Y combinator \\
63& 190 & $x^{\dagger}$ & Superscript cross & Superscript cross & Language isomorphism \\

@@

64& 213 & $\tau'<:\tau$ & Subtype & $\tau'$ is a subtype of $\tau$ & $\tau'$ is a subtype of $\tau$ \\

@@

65& 252 & $()^{\ddagger}$ & Isomorphism & Isomorphism & $()^{\ddagger}$ is a method isomorphism \\

@@

66& 257 & $k \vartriangleright e$ & Right triangle & Evaluation state & Evaluate $e$ on $k$ \\
67& 257 & $k \vartriangleleft e$ & Left triangle & Return state & Evaluate $k$ on $e$\\
68& 258 & $\epsilon$ & Epsilon & Empty frame & Empty frame\\
69& 258 & (\textemdash) & Frame hole & Frame hole & A place to put an evaluated expression into a frame\\
70& 258 & $k;f$ & Stack with frame & Stack $k$ with frame $f$  & Stack $k$ has frame $f$ at the bottom\\
71& 259 & $k \vartriangleleft:\tau$ & Triangle colon & Stack $k$ expects value of type $\tau$ & Stack $k$ expects value of type $\tau$\\
72& 259 & $f:\tau\rightsquigarrow\tau'$ & Squiggle arrow & Transform & Frame $f$ transforms expression of type $\tau$ into expression of type $\tau'$\\
73& 261 & $s \looparrowright e$ & Loop arrow & Unravel & State $s$ goes to expression $e$ \\
74& 261 & $k \bowtie e = e'$ & Bowtie & Goes to & Stack $k$ and expression $e$ goes to expression $e'$\\

@@

75& 266 & $k \blacklozenge$ & Dark left triangle & Failed & Stack $k$ is in a failed state \\

@@

76 & 282 & $a \sim \tau$ & Tilde & Define $a$ & Define symbol $a$ as type $\tau$ \\
77 & 282 & $\Sigma$ & Sigma & Symbol context & Set of symbol definitions \\
78 & 284 & $'a$ & Quote & Symbol reference & Symbol reference \\
\end{tabular}

\subsubsection*{32 Fluid Binding}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\
79 & 290 & $\mu ' \otimes a \hookrightarrow e$ & Circle times & Extended by &  Map symbol $a$ to expression $e$\\
80 & 290 & $\mu ' \otimes a \hookrightarrow \bullet$ & Circle times & Extended by &  Symbol $a$ is undefined\\
81 & 290 & $\mu ' \otimes a \hookrightarrow $ \underline{ } & Circle times & Extended by &  Symbol $a$ is indeterminate\\

@@

82& 308 & $x \leftarrow e ; m$ & Left arrow & Sequence & Execute command $m$ with $e$ substituted for $x$ \\
83& 308 & $a := e$ & Colon equals & Assign & Assign $e$ to $a$\\
84 & 308 & $*a$ & Star & Contents & Get the value of $a$\\
85 & 309 & $ m \| \mu $& State & State & Command $m$ with memory map $\mu$\\
86 & 314 & $ m \thicksim \tau$ & Dotted tilde & Dotted tilde & Command $m$ returns a value of type $\tau$\\
\end{tabular}

@@

87 & 320 & $ \& a $ & Ampersand & Reference & Reference to assignable \\

@@

88 & 333 & $ \Longrightarrow $ & Long right arrow & Implies & Implication (low precedence) \\

\subsection*{XV. Parallelism}
\subsubsection*{37 Nested Parallelism}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

89& 344 & $c_1 \otimes c_2 $ & Circle times  & Parallel cost & Cost of executing in parallel \\
90& 344 & $c_1 \oplus c_2 $ & Circle plus  & Sequential cost & Cost of executing in sequence \\
91& 350 & $a_1 \hookrightarrow s_1 \otimes a_2 \hookrightarrow s_2$ & Circle times  & Parallel join & Join local states \\
\end{tabular}

\subsection*{XVI. Concurrency and Distribution}
\subsubsection*{39 Process Calculus}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

92& 365 & $ \$ E$ & Dollar  & Synchronize & Synchronize parallel processes \\
93& 365 & $E_1 + E_2 $ & Plus  & Choice & Pick one of 2 expressions \\
94& 365 & $?a;P$ & Query  & Query & Query a channel \\
95& 365 & $!a;P$ & Bang  & Signal & Signal a channel \\
96 & 367 & $ P_1 \otimes P_2 $  & Circle times & Composition & Compose 2 concurrent processes \\
97 & 367 & $P \overset{\alpha}{\longmapsto} P' $ & Maps to & Steps & $P$ steps to $P'$ if action $\alpha$ is permissible \\
98 & 369 & $ *P $  & Star & Replication & Replicate process $P$ \\
99 & 370 & $ \nu a . P $ & Nu & New channel & Declare new channel $a$ in process $P$ \\
100 & 371 & $P \overset{\alpha}{\underset{\Sigma}{\longmapsto}} P' $ & Maps to & Steps & $P$ steps to $P'$ if action $\alpha$ is permissible in context $\Sigma$ \\
101 & 373 & $ ! a ( e ; P ) $  & Bang & Send & Send expression $e$ on channel $a$ to process $P$ \\
102 & 373 & $ ? a ( x . P ) $  & Query & Receive & Receive expression $e$ on channel $a$ in process $P$ \\
103 & 376 & $ \tau $ chan & Tau & Channel type & Channel of type $\tau$ \\
104 & 376 & $ \& a $ & Ampersand & Channel reference & Reference to channel $a$ \\
105 & 376 & $ !!(e_1;e_2;P) $ & Bang bang & Send & Send message on channel $e_1$  \\
106 & 376 & $ ??(e;x.P) $ & Query query & Receive & Receive message on channel $e$  \\
107 & 377 & $ @ $ & At & Map & Maps lambda expressions to PiC \\
\end{tabular}

\subsubsection*{40 Concurrent Algol}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

108& 382 & $ P_1 \otimes P_2 $ & Circle times  & Concurrent & Run processes $P_1$ and $P_2$ concurrently \\
109 & 382 & $ \nu a ~\tau . p $ & Nu & New channel & Create a new chanell \\
110 & 383 & $ m \overset{\alpha}{\underset{\Sigma}{\Rightarrow}} \nu \Sigma ' \{ m' \otimes p'\} $ & Fat right arrow & Transitions & Command $m$ transitions to command $m'$ while creating new channels $\Sigma$  and
new processes $p'$ . The action $\alpha$ specifies the interactions of which $m$ is capable when executed. \\
\end{tabular}

\subsubsection*{41 Distributed Algol}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

111 & 392 & $ a~\tau @ w $ & Tilde  & Declare & $a$ is a channel at site $w$ carrying payloads of type $\tau$ \\
\end{tabular}

\subsection*{XVII. Modularity}

\subsubsection*{43 Singular Kinds and Subkinding}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\
112 & 407 & $ c::k $ & Colon colon  & Define constructor &  Define constructor $c$ of kind $k$\\
113 & 407 & $ k_1<::k_2 $ & Less than colon colon  & Subkind & Kind $k_1$ is a subkind of kind $k_2$\\
